### 2018-05-13 Paper/method.tex
...
..

\clearpage

\begin{breakablealgorithm}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
    \Procedure{Screening}{}
      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
       according to the probability density $\bm{f(\theta)}$.
       \State $N_t = N_t + n_1$
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$.

@@

@@

%\begin{breakablealgorithm}
%  \caption{Parameter screening with DGSMs: A generalized approach.}
%  \begin{algorithmic}[1]
%    \Procedure{Screening}{}
%      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
%       according to the probability density $\bm{f(\theta)}$.
%      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
%             $k = 1, \ldots, n_1$. 
%
%      \State Compute 
%      $\mu_{1, i} = \frac{1}{n_1} \sum_{k = 1}^{n_1} (g^k_i)^2$
%      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
%             $i = 1, \ldots, \Np$. 
%      \State Determine initial ranks: 
%            let $\mathcal{R}^{old} = \{ \theta_{\sigma(i)}\}_{i=1}^{n_1}$ such that 
%\[
%   \nu_{\sigma(1)} \geq \nu_{\sigma(2)} \geq \cdot \geq \nu_{\sigma(\Np)}. 
%\]
%      \State Set $s$ = 1.
%      \State Set $\mathrm{done} = \mathrm{false}$.
%      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
%        \State Set $s = s + 1$.
%        \State Draw $n_s$ new samples 
%                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
%        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
%             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.
%
%        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
%               $\{\bm{g}_k \}_{k = 1}^{n_{s-1}+n_s}$.
%        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
%        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
%        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
%               \left(\frac{|\mu_{i,s} - \mu_{i,s-1}|}{ \mu_{i,s-1}}\right)$.
%      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
%         \State $\mathrm{done} = \mathrm{true}$
%      \Else
%          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
%      \EndIf
%    \EndWhile
%    \State Let $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \nu_i \ni \displaystyle\frac{\nu_i}{\max(\bm{\nu})}> \tau_\text{screen}\}.$
%    
%    \EndProcedure
%  \end{algorithmic}
%  \label{alg:screen}
%\end{breakablealgorithm}

@@

\node (qoi) [io, below of=start,align=left] {Select an appropriate model output};

\draw [arro] (start) -- (qoi);

\node (tol) [io, below of=qoi, text width=9em,align=left,yshift=-0.2cm] {Initialize: $\tau$, $\tau_\text{screen}$, 
$s_\text{max}$, $N_t$ = 0};

@@

\node (screen) [process, below of=tol, text width=9.5em] {Parameter Screening};

\draw [arro] (tol) -- (screen);

\node (output) [process, below of=screen, text width=9.5em] {Compute $\alpha$ based on $\mathcal{I}_\text{active}$};

\draw [arro] (screen) -- (output);

\node (dr) [draw, diamond, aspect=1.5,yshift=-8.4cm, text width=4.5em, text centered] {If $\alpha < 1$};

\draw [arro] (output) -- (dr);

\node (fss) [process, right of=dr, text width=9em,xshift=3.5cm] {Construct full-space surrogate (FSS)};

\draw [arro] (dr) -- node[anchor=south] {N} (fss);

\node (res) [draw, diamond, aspect=1.5, xshift=3.5cm,text width=4.5em, text centered, right of=fss] {FSS converged$?$};

\draw [arro] (fss) -- (res);

\node (dtol) [io, above of=res, text width=8.7em,align=left,yshift=2.8cm] {Update: $\tau$, $s_\text{max}$, $N_t$};

\draw [arro] (dtol) -| (screen);

 \draw [arro] (res) -- node[anchor=east,yshift=-0.6cm] {N} (dtol);

 \node (assess) [process, below of=dr, text width=11em,yshift=-1.2cm] {If applicable, assess $\alpha$ and convergence
  of FSS};

 \draw [arro] (dr) -- node[anchor=east] {Y}(assess);

 \node (con) [draw, diamond, aspect=1.5,text width=4em, text centered, below of=assess,yshift=-0.7cm] {Continue$?$};

 \draw [arro] (assess) -- (con);

\node (ros) [process, below of=con, text width=6em, yshift=-0.7cm] {Construct the ROS};

 \draw [arro] (con) -- node[anchor=east] {Y}(ros);

\node (verify) [process, below of=ros, text width=9em,yshift=-0.2cm] {Verify accuracy of the surrogate};

\draw [arro] (ros) -- (verify);

\node (stop) [startstop, right of=verify,xshift=3.5cm] {Stop};

\draw [arro] (verify) -- (stop);

\draw [arro] (res) |- node[anchor=east,yshift=6.9cm] {Y} (stop);

\draw [arro] (con) -| node[anchor=south,xshift=-3cm] {N} (stop);

>>>>

\clearpage
\iffalse
\begin{breakablealgorithm}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
    \Procedure{Screening}{}
      \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
       according to the probability density $\bm{f(\theta)}$.
      \State $N_t = N_t + n_1$
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$.

@@

    \EndProcedure
  \end{algorithmic}
  \label{alg:screen}
\end{breakablealgorithm}
\fi

%%%%%%%%%%%

\begin{breakablealgorithm}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
  \caption{Parameter screening with DGSMs: A generalized approach.}
  \begin{algorithmic}[1]
\Require $\tau > 0$, $\tau_\text{screen} > 0$,
$s_\text{max}$, $\beta > 0$, $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$. 
\Ensure $\mathcal{I}_\text{active}$, $\{ \bm{g}^k \}_{k=1}^{N_\text{total}}$, $N_\text{total}$. 
    \Procedure{Screening}{}
    %  \State Draw samples $\{ \bm{\theta}_k \}_{k = 1}^{n_1}$ 
     %  according to the probability density $\bm{f(\theta)}$.
     %   \State $N_\text{total} = N_\text{total} + n_1$.
      \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$, 
             $k = 1, \ldots, n_1$.

      \State Compute 
      $\mu_{1, i} = \frac{1}{N_\text{total}} \sum_{k = 1}^{N_\text{total}} (g^k_i)^2$
      \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{1,i}}$, for each $\theta_i$, 
             $i = 1, \ldots, \Np$. 
      \State Determine initial ranks: 
            let $\mathcal{R}^{old} = \{ \nu_{i_1}, \nu_{i_2}, \ldots, \nu_{i_\Np}\}$ such that 
\[
   \nu_{i_1} \geq \nu_{i_2} \geq \cdots \geq \nu_{i_\Np}. 
\]
      \State Set $s$ = 1.
      \State Set $\mathrm{done} = \mathrm{false}$.
      \While {$\mathrm{done} == \mathrm{false}$ \textbf{AND} $s \leq s_\text{max}$} 
        \State $s = s + 1$.
        \State Draw $n_s = \lceil \beta n_1 \rceil$ new samples 
                  $\bm{\theta}_k$, $k = n_{s-1} + 1, \ldots, n_{s-1} + n_s$
       \State $N_\text{total} = N_\text{total} + n_s$.
        \State Compute $\bm{g}^k = \nabla_{\bm{\theta}}G(\bm\theta_k)$,
             $k = n_{s-1}+1, \ldots, n_{s-1}+n_s$.

        \State Compute $\{ \mu_{s,i} \}_{i=1}^\Np$ using the augmented sample 
               $\{\bm{g}_k \}_{k = 1}^{N_\text{total}}$.
        \State Compute $\nu_i = \widehat{\mathcal{C}_i\mu_{s,i}}$, $i = 1, \ldots \Np$.
        \State Determine new ranks $\mathcal{R}^{new}$ based on $\{\nu_i\}_{i=1}^\Np$. 
        \State Compute $\displaystyle\Delta\mu_s = \max_{1\leq i \leq \Np}
               \left(\frac{|\mu_{s,i} - \mu_{s-1,i}|}{ \mu_{s-1,i}}\right)$.
      \If {$\mathcal{R}^{\tiny{new}} = \mathcal{R}^{\tiny{old}}$ {\bf AND}  $\Delta\mu_s \leq \tau$}
         \State $\mathrm{done} = \mathrm{true}$
      \Else
          \State Set $\mathcal{R}^{old} = \mathcal{R}^{new}$
      \EndIf
    \EndWhile
    \State $\mathcal{I}_\text{active} = \{ i \in \{1, \ldots, \Np\} : \displaystyle\frac{\nu_i}
        {\|\bm{\nu}\|_\infty} > \tau_\text{screen}\}.$

@@

@@

\node (val) [process, below of=start, text width=14.5em] {Construct a validation test suite using
pre-allocated resources.};

\draw [arro] (start) -- (val);

\node (qoi) [io, below of=val,align=left,yshift=-0.2cm] {Select an appropriate model output};

\draw [arro] (val) -- (qoi);

\node (tol) [io, below of=qoi, text width=9em,align=left,yshift=-0.2cm] {Initialize: $\tau$, $\tau_\text{screen}$, 
$s_\text{max}$, $\beta$, $N_\text{total}$ = 0};

@@

\node (sam0) [process, below of=tol, text width=12.5em, yshift=-0.3cm] {Draw $n_0$ samples $\{ \bm{\theta}_k \}_{k = 1}^{n_0}$ 
     according to $\bm{f(\theta)}$};

\draw [arro] (tol) -- (sam0);

\node (counter) [process, below of=sam0, text width=9.5em, yshift=-0.21cm] {\vspace{-6mm}\be N_\text{total} = N_\text{total} + n_0 \nonumber\ee};

\draw [arro] (sam0) -- (counter);

\node (fss) [process, below of=counter, text width=14.5em, yshift=-0.28cm] {Construct regression-based 
surrogate in full-space (FSS) uing $N_\text{total}$ model evaluations};

\draw [arro] (counter) -- (fss);

\node (chk) [process, below of=fss, text width=12.5em, yshift=-0.5cm] {Assess accuracy of FSS using the
validation test suite};

\draw [arro] (fss) -- (chk);

\node (res) [draw, diamond, aspect=1.5, text width=7.5em, text centered, below of=chk,yshift=-1.5cm] {Is \\ FSS, 
sufficiently accurate$?$};

\draw [arro] (chk) -- (res);

\node (screen) [process, right of=res, text width=9.5em, xshift=4.5cm] {Parameter Screening};

\draw [arro] (res) -- node[anchor=north] {N} (screen);

\node (dr) [draw, diamond, aspect=1.8, text width=7.5em, text centered, right of=screen,xshift=4cm] {Is $\alpha$
small enough$?$};

\draw [arro] (screen) -- (dr);

\node (dtol) [io, above of=dr, text width=8.7em,align=left,yshift=3.2cm] {Update: $\tau$, $\tau_\text{screen}$, 
$s_\text{max}$, $\beta$};

\draw [arro] (dr) -- node[anchor=east,yshift=-0.8cm] {N} (dtol);

\draw [arro] (dtol) |- (sam0);

\node (ros) [process, below of=dr, text width=11.5em, yshift=-1.5cm] {Construct a reduced-order surrogate (ROS)};

\draw [arro] (dr) -- node[anchor=east,yshift=0.1cm] {Y} (ros);

\node (ver) [process, left of=ros, text width=14.5em, xshift=-5cm] {Verify ROS using evaluations at $N_\text{total}$
$\&$ the validation test suite};

\draw [arro] (ros) -- (ver);

\node (stop) [startstop, below of=chk,yshift=-4.5cm] {Stop};

\draw [arro] (res) -- node[anchor=east,yshift=0.0cm] {Y} (stop);

\draw [arro] (ver) -- (stop);
